\documentclass[ 12pt ]{article}
\usepackage{amsmath, amsthm, amssymb, csquotes, enumitem, extpfeil, graphicx, listings, mathrsfs, tikz-cd}
\usepackage[margin=0.5in]{geometry}
\graphicspath{ ./ }

\begin{document}

\noindent Landon Fox \\
\noindent Math 731, Modern Algebra \\
\noindent November 10, 2021

\begin{center}
\Large Homework 7
\end{center}

\begin{enumerate}
	% problem 1
	\item[\textbf{1.}] Let $A$ be a left $R$-module and $f : A \to A$ an $R$-module homomorphism with $ff = f$. Show that then $$A \cong \mathrm{ker}\, f \oplus \mathrm{im}\, f.$$

		\begin{proof}
			Let $A$ be a left $R$-module and $f : A \to A$ an $R$-module homomorphism with $ff = f$. Provided that $\mathrm{ker}\, f$ and $\mathrm{im}\, f$ are modules in their own right, consider the following homomorphisms
			\begin{align*}
				&\pi_1 : A \to \mathrm{ker}\, f, & \iota_1 : \mathrm{ker}\, f \to A \\
				&\pi_2 : A \to \mathrm{im}\, f, & \iota_2 : \mathrm{im}\, f \to A,
			\end{align*}
			defined as
			\begin{align*}
				&\pi_1(a) = f(a) - a, & \iota_1(a) &= f(a) - a, \\
				&\pi_2(a) = f(a), & \iota_2(a) &= a,
			\end{align*}
			for all $a \in A$ in their respective domains. Observe that the functions above are linear; indeed,
			\begin{align*}
				&\pi_1(a + b) = f(a + b) - (a + b) = \pi_1(a) + \pi_1(b), & \pi_1(ra) &= f(ra) - ra = r(f(a) - a) = r\pi_1(a), \\
				&\pi_2(a + b) = f(a + b) = f(a) + f(b) = \pi_2(a) + \pi_2(b), & \pi_2(ra) &= f(ra) = rf(a) = r\pi_2(a), \\
				&\iota_2(a + b) = a + b = \iota_2(a) + \iota_2(b), & \iota_2(ra) &= ra = r\iota_2(a),
			\end{align*}
			for all $r \in R$ and $a, b \in A$ in their respective domains by the linearity of $f$. By a similar argument, we can see that $\iota_1$ is also linear. We now show that $$\pi_1 \iota_1 = \mathrm{id}_{\mathrm{ker}\, f},\;\; \pi_2 \iota_1 = 0,\;\; \pi_2 \iota_2 = \mathrm{id}_{\mathrm{im}\, f},\;\; \pi_1 \iota_2 = 0,\;\; \mathrm{and}\;\; \iota_1 \pi_1 + \iota_2 \pi_2 = \mathrm{id}_A,$$ hence, proving the result. First let $a \in \mathrm{ker}\, f$, then it follows that
			\begin{align*}
				\pi_1 \iota_1(a) &= \pi_1(f(a) - a) & \pi_2 \iota_1(a) &= \pi_2(f(a) - a) \\
				&= f(f(a) - a) - (f(a) - a) & &= f(f(a) - a) \\
				&= f(f(a)) - f(a) - f(a) + a & &= f(f(a)) - f(a) \\
				&= f(a) - f(a) - f(a) + a & &= f(a) - f(a) \\
				\pi_1 \iota_1(a) &= a & \pi_2 \iota_1(a) &= 0.
			\end{align*}
			Similarly, if $a \in A$, we can see that
			\begin{align*}
				\pi_2 \iota_2(f(a)) &= \pi_2(f(a)) & \pi_1 \iota_2(f(a)) &= \pi_1(f(a)) \\
				&= f(f(a)) & &= f(f(a)) - f(a) \\
				\pi_2 \iota_2(f(a)) &= f(a) & &= f(a) - f(a) \\
				& & \pi_1 \iota_2(f(a)) &= 0.
			\end{align*}
			Lastly, observe that
			\begin{align*}
				(\iota_1 \pi_1 + \iota_2 \pi_2)(a) &= \iota_1 \pi_1(a) + \iota_2 \pi_2(a) \\
				&= \iota_1(f(a) - a) + \iota_2(f(a)) \\
				&= f(f(a) - a) - (f(a) - a) + f(a) \\
				&= f(f(a)) - f(a) - f(a) + a + f(a) \\
				&= f(a) - f(a) + a \\
				(\iota_1 \pi_1 + \iota_2 \pi_2)(a) &= a
			\end{align*}
			for all $a \in A$. Thus, $A \cong \mathrm{ker}\, f \oplus \mathrm{im}\, f$.
		\end{proof}


	% problem 2
	\item[\textbf{2.}] Show that an $R$-module is irreducible if and only if it is a cyclic module, with any nonzero element as generator.

		\begin{proof}
			Let $A$ be an $R$-module. Suppose $A$ is irreducible and $a \in A$ an arbitrary nonzero element. Since the only nonzero submodule of $A$ is $A$ itself, it holds that $(a) = A$ by definition. Conversely, let $A$ be a cyclic module, generated by any nonzero element. Let $B \subseteq A$ be a nonzero submodule of $A$ and $a \in B$ a nonzero element of the submodule. Observe that $(a) \subseteq B$; indeed, since $a \in B$, we have that $ra + n \cdot a \in B$ for all $r \in R$ and $n \in \mathbb{Z}$ and so $$(a) = \{ ra + n \cdot a : r \in R, n \in \mathbb{Z} \} \subseteq B.$$ Provided that $(a) = A$, it follows that $B = A$ as desired.
		\end{proof}



	% problem 3
	\item[\textbf{3.}] Let $A \xrightarrow{f} B \xrightarrow{g} C \to 0$ and $0 \to C \xrightarrow{h} D \xrightarrow{k} E$ be exact sequences of $R$-modules. Show that then the sequence $A \xrightarrow{f} B \xrightarrow{hg} D \xrightarrow{k} E$ is also exact.

		\begin{proof}
			Consider the two exact sequences of $R$-modules defined above. We will show that $\mathrm{im}\, f = \mathrm{ker}\, hg$ and $\mathrm{im}\, hg = \mathrm{ker}\, k$. Let $a \in A$, then $$hg(f(a)) = h(g(f(a))) = h(0) = 0,$$ providing $\mathrm{im}\, f \subseteq \mathrm{ker}\, gh$ given that $\mathrm{im}\, f = \mathrm{ker}\, g$. We know that for $0 \to C \xrightarrow{h} D$ to be exact, $h$ must be monic; therefore, if $h(g(b)) = 0$ for some $b \in B$; it must hold that $g(b) \in \mathrm{ker}\, h = \{ 0 \}$. Hence, $$\mathrm{im}\, f = \mathrm{ker}\, g \supseteq \mathrm{ker}\, hg.$$ Now, let $b \in B$ and observe that $$k(hg(b)) = k(h(g(b))) = 0$$ since $\mathrm{im}\, h = \mathrm{ker}\, k$. Next, for $B \xrightarrow{g} C \to 0$ to be exact, $g$ must be epic. Furthermore, if $d \in \mathrm{ker}\, k = \mathrm{im}\, h$ we have a $c \in C$ such that $d = h(c)$ as well as a $b \in B$ such that $c = g(b)$ and so $d = hg(b) \in \mathrm{im}\, hg$.
		\end{proof}



\end{enumerate}

\end{document}
